Rule learning for verification from temporal data

### 2016-08-30 Travis/main.tex
intro

\title{Rule learning from classified temporal data}
\subtitle{Plan of Attack}

\authorinfo{Mark Santolucito}           {Yale University}           {mark.santolucito@yale.edu}
\authorinfo{Name2\and Name3}           {Affiliation2/3}           {Email2/3}

@@

\begin{abstract}
Rule based classification is an effective machine learning technique that yields low misclassification rates.
However, building a rule based system requires manual creation of large databases of logical constraints.
We present a method to generate rule based systems from temporally structured data.
As an demonstration of this algorithm, we implement a learner to automatically generate constraints for the TravisCI testing framework.
The algorithm runs over Github commit histories to generate logical constraints that allow us to detect potential build errors without actually building, saving valuable programmer and server time.
\end{abstract}

@@

@@

From this summary we can then build a model $M(P_t)$, which is the full set of possible rules derivable from the model.
These possible rules must be given by the user.
In \cite{CAV}, these were called Attributes, and express constraints such as, ordering of lines, or substring relations on values.

>>>>

\title{Rule learning for verification from temporal data}
\subtitle{Plan of Attack}

\authorinfo{Mark Santolucito}           {Yale University}           {mark.santolucito@yale.edu}
%\authorinfo{Name2\and Name3}           {Affiliation2/3}           {Email2/3}

@@

\begin{abstract}
Rule based classification is an effective machine learning technique that yields low misclassification rates.
However, building a rule based system requires manual creation of large databases of logical constraints.
We present a method to generate rule based systems from temporally structured data.
As an demonstration of this algorithm, we plan to implement a learner that automatically generates constraints for the TravisCI testing framework.
The algorithm will utilize Github commit histories to generate logical constraints that allow us to detect potential build errors without actually building, saving valuable programmer and server time.
\end{abstract}

@@

Machine learning is a new direction in verification\cite{Santolucito2016,ETH_Guy}.
However, algorithms such as neural nets and n-gram models lead to probabilistic models of correctness.
While often effective in practice, these do not provide the true guarantees of a traditional verification approach.
In addition, these tools often cannot provide a justification for the output.
Neural nets behave surprisingly similarly to human brains, and providing proofs to conclusions is equally challenging.

Version space learning \cite{lau2000version}.

@@

From this summary we can then build a model $M(P_t)$, which is the full set of possible rules derivable from the model.
These possible rules must be given by the user.
In \cite{Santolucito2016}, these were called Attributes, and express constraints such as, ordering of lines, or substring relations on values.
